################ CALCIUM ANALYSIS WITHOUT THRESHOLDING
```{r libraries, include=FALSE}
# Libraries ---------------------------------------------------------------
library(utils)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(plotly)
library(tidyr)
library(reshape2)
# library(heatmaply)
library(factoextra)
library(ggdendro)
library(grid)
library(RcppCNPy)
library(cowplot)
library(ggpubr)
library(mmand)
library(rstudioapi)
# Load raw Suite2p npy arrays using reticulate
library(reticulate)
options(reticulate.conda_binary = "/Users/simo/miniforge3")
```

```{r echo=FALSE, setup, include=FALSE}
knitr::opts_knit$set(root.dir = selectDirectory(caption = "Select suite2p/plane folder", 
                           label = "Select"))
```

```{r script}
getwd()
np <-import("numpy")

# all script from stat.npy
# Stat.npy ----------------------------------------------------------------
stat <- np$load("stat.npy", allow_pickle = TRUE) #stats containing ROIs XY
# Loop over stat.npy to access "med" (ROIs coordinates) to create list of cells coordinates. ROIs from suite2p starts with index 0
posXY <- data.frame()
for (i in 1:length(stat)) {
  posXY <- rbind(posXY, stat[[i]][["med"]])
}

posXY$Cell <- as.numeric(0:(nrow(posXY)-1))
colnames(posXY) <- c('Y','X','Cell')


redcell <- np$load("redcell.npy", allow_pickle = TRUE) #load redcell.npy
posXY$redcell <- redcell[,1]



# iscell.npy --------------------------------------------------------------
#iscell.npy to select only ROIs that are recognized as cells
iscell <- as.data.frame(np$load("iscell.npy", allow_pickle = TRUE))
iscell$Cell <- as.numeric(0:(nrow(iscell)-1))
posXY$Positive <- iscell$V1
posXY <- subset(posXY, Positive == 1, select = c(Y,X,Cell,redcell))
positives <- posXY$Cell
positivesPLUSone <- positives+1 ##this is needed because suite2p starts counting ROIs with the number 0 (python..)



# spks.npy ----------------------------------------------------------------
# load suite2p numpy arrays outputs
spks <- as.data.frame(np$load("spks.npy", allow_pickle = TRUE)) #deconvolved peaks
spks[is.na(spks)] <- 0 #NAs replaced with 0

#need to clean it from first 0 and select best window
spks <- spks[,50:ncol(spks)]


spks <- t(apply(spks, 1, function(x) (x - min(x))/(max(x)-min(x)))) # Normalize each cell
spks <- spks[positivesPLUSone,] #select only positives (real cells)
rownames(spks) <- positives #fix rownames with actual cells numbers

spks[is.na(spks)] <- 0 #NAs replaced with 0

saveRDS(spks, file = "~/calcium-clustering/data/ID0032_spks.rds")
write.csv(spks, "~/calcium-clustering/data/ID0032_spks.csv")

# Cutoff function <- anything below 2*(row sd/cell) is 0, anytlong above is 1
cutoff <- function(x) {
  th <- 2*sd(x)
  x[x < th] <- 0
  x[x > th] <- 1
  return(x)
}

spksthresholded <- t(apply(spks, 1, cutoff))
saveRDS(spksthresholded, file = "~/calcium-clustering/data/ID0032_spksthresholded.rds")
write.csv(spksthresholded, "~/calcium-clustering/data/ID0032_spksthresholded.csv")



## CALCULATE ALL ACTIVE CELLS OVER TIME
# Calculating percentage of active cells over time -------------------------
spksSUM <- colSums(spksthresholded)
spksSUM <- as.data.frame(spksSUM)
spksSUM$Time <- 0:(nrow(spksSUM)-1)
spksSUM$Perc <- spksSUM$spksSUM/nrow(spksthresholded)*100
saveRDS(spksSUM, file = "~/calcium-clustering/data/ID0032_spksSUM.rds")
write.csv(spksSUM, file = "~/calcium-clustering/data/ID0032_spksSUM.csv")
spksSUM.plt <- ggplot(spksSUM, aes(Time, Perc))+
  geom_line()+ 
  theme_pubr()


# Frequency -cell thresholded events divided by 60 sec -----
posXY$frequency <- rowSums(spksthresholded)/60 #events per minute
frequency <- mean(rowSums(spksthresholded)/60)

saveRDS(frequency, file = "~/calcium-clustering/data/ID0032_mean_frequency.rds")
write.csv(frequency, file = "~/calcium-clustering/data/ID0032_mean_frequency.csv")
# Compare number of events/min across samples?



# Spectrum analysis. Spectrum() automatically removes a linear trend from the time series






# # Plot total calcium activity/time --------------------------------------
spksSUM2 <- colSums(spks)
spksSUM2 <- as.data.frame(spksSUM2)
spksSUM2$Time <- 0:(nrow(spksSUM2)-1)
spksSUM2$Mean <- spksSUM2$spksSUM2/nrow(spksSUM2)
saveRDS(spksSUM2, file = "~/calcium-clustering/data/ID0032_spksSUM2.rds")
write.csv(spksSUM2, file = "~/calcium-clustering/data/ID0032_spksSUM2.csv")
spksSUM2.plt <- ggplot(spksSUM2, aes(Time, Mean))+
  geom_line()+ 
  theme_pubr()+
  geom_smooth()+
  ylab("Ca2+")+
  ylim(0, NA)
spksSUM2.ylim <- layer_scales(spksSUM2.plt)$y$get_limits()
spksSUM2.plt



# Average activity PER CELL (deconvolved peaks) ---------------------------
posXY$Mean <- rowMeans(spks)


# # Raster+dendro all cells/time ggplot ------------------------------------------
dfpeaks <- as.data.frame(t(spks))  # Doing this coercion will apply +1 to all cells numbers
# colnames(dfpeaks) <- 1:ncol(dfpeaks)
dfpeaks$time <- 0:(nrow(dfpeaks)-1)
meltPeaks <- melt(dfpeaks, id = "time")
colnames(meltPeaks) <- c('time','cell','Ca2+')


# Hierarchical clustering
hc <- hclust(dist(spks, method = "euclidean"), method = "ward.D2")
dhc <- as.dendrogram(hc)

# Dendrogram
peaks.dendro <- ggdendrogram(dhc, rotate = TRUE, labels = FALSE)+
                  theme(panel.grid = element_blank(),
                        axis.title.y = element_blank(),
                        axis.text.x = element_blank(),
                        axis.text.y = element_blank(),
                        axis.ticks = element_blank())

# GRID to put together dendrograms and rasters
peaks.order <- order.dendrogram(dhc)

## Order the levels according to their position in the cluster
peaks.rows <- rownames(spks)
peaks.rows <- as.data.frame(peaks.rows)
meltPeaks$cell <- factor(x = meltPeaks$cell,
                         levels = peaks.rows$peaks.rows[peaks.order], 
                         ordered = TRUE)
# Mark RFP+ cells
RFPcells <- posXY %>% 
                      subset(redcell==1) %>%
                        .$Cell # extract redcell indexes
meltPeaks$RFP <- meltPeaks$cell %in% RFPcells

# Ggplot raster with dendro order
raster.hc <- ggplot(meltPeaks, aes(time, cell))+
  geom_raster(aes(fill = `Ca2+`))+
  geom_line(aes(color = RFP), alpha = .2)+
  scale_fill_gradientn(colours=c("white", "black"))+
  scale_color_manual(values = c("TRUE" = "red",
                                "FALSE" = "white"))+
  theme_pubr()+
  ylab("cell ID")+
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        plot.title = element_text(colour = "red", hjust = .5))
  # ggtitle("ID0032 hclust", subtitle = sprintf("Mean frequency is: %s events/min", round(frequency, digits = 3)))

# GRID raster/sums
plots <- align_plots(raster.hc, spksSUM.plt, align = 'v', axis = 'l')
grid <- plot_grid(plots[[1]], spksSUM.plt, ncol = 1, rel_heights = c(4.5,1))

# Save data
ggsave(plot = grid, file = "/Users/Simo/calcium-clustering/plots/ID0032.grid-allcells.png", 
       device = "png",  bg = "white",
       width = 20, height = 15, units = "cm", dpi = 320,
       scale = 2)
saveRDS(posXY, file = "~/calcium-clustering/data/ID0032_posXY.rds")
write.csv(posXY, file = "~/calcium-clustering/data/ID0032_posXY.csv")

########################################### RFP ####################################
# RFPcells <- unique(scan("RFPcells.R", sep = ","))


# Calculating percentage of active RFP cells over time (using deconvolved peaks)--------------------

RFPt <- subset(spksthresholded, rownames(spksthresholded) %in% RFPcells) #select only RFP cells

# Isolate RFP+ XY from posXY dataframe ------------------------------------
posXY$RFP <- posXY$Cell %in% RFPcells

posXY.RFP <- posXY %>%
                      subset(redcell==1)

# Frequency -cell thresholded events divided by 60 sec -----
posXY.RFP$frequency <- rowSums(RFPt)/60 #events per minute
frequency.RFP <- mean(rowSums(RFPt)/60)

saveRDS(posXY.RFP, file = "~/calcium-clustering/dataposXY.RFP.rds")
write.csv(posXY.RFP, file = "~/calcium-clustering/dataposXY.RFP.csv")

##ggplot to show percentage of coactive RPF+ cells over time
RFPsum <- as.data.frame(colSums(RFPt))
RFPsum$Time <- 0:(nrow(RFPsum)-1)
RFPsum$Perc <- RFPsum$`colSums(RFPt)`/nrow(RFPt)*100
saveRDS(RFPsum, file = "~/calcium-clustering/data/ID0032_RFPsum.rds")
write.csv(RFPsum, file = "~/calcium-clustering/data/ID0032_RFPsum.csv")

# Plot
RFPsum.plt <- ggplot(RFPsum, aes(Time, Perc))+
  geom_line()+
  theme_pubr()



# Sum of all activity over time RFP+ --------------------------------------
RFP <- subset(spks, rownames(spks) %in% RFPcells) #select only RFP cells
RFPsum2 <- as.data.frame(colSums(RFP)/nrow(RFP)) #normalized by number of RFP cells
RFPsum2$Time <- 0:(nrow(RFPsum2)-1)
saveRDS(RFPsum2, file = "~/calcium-clustering/data/ID0032_RFPsum2.rds")
write.csv(RFPsum2, file = "~/calcium-clustering/data/ID0032_RFPsum2.csv")

RFPsum2.plt <- ggplot(RFPsum2, aes(Time, `colSums(RFP)/nrow(RFP)`))+
  geom_line()+
  theme_pubr()+
  geom_smooth()+
  ylab("Deconvolved activity")+
  ylim(0, NA)
RFPsum2.plt.ylim <- layer_scales(RFPsum2.plt)$y$get_limits()


# RFPcells for activity/hc/raster/dendrogram.  -------------------------------
## Take care of using already normalized spks array
# Raster ggplot
dfpeaks.RFP <- as.data.frame(t(RFP))
# colnames(dfpeaks.RFP) <- 1:ncol(dfpeaks.RFP)
dfpeaks.RFP$time <- 0:(nrow(dfpeaks.RFP)-1)
meltPeaks.RFP <- melt(dfpeaks.RFP, id = "time")
colnames(meltPeaks.RFP) <- c('time','cell','Ca2+')

# Hierarchical clustering
hc.RFP <- hclust(dist(RFP, method = "euclidean"), method = "ward.D2")
dhc.RFP <- as.dendrogram(hc.RFP)

# Dendrogram
RFP.dendro <- ggdendrogram(dhc.RFP, rotate = TRUE, labels = FALSE)+
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank())

# GRID to put together dendrograms and rasters
RFP.order <- order.dendrogram(dhc.RFP)

## Order the levels according to their position in the cluster
RFP.rows <- rownames(RFP)
RFP.rows <- as.data.frame(RFP.rows)
meltPeaks.RFP$cell <- factor(x = meltPeaks.RFP$cell,
                         levels = RFP.rows$RFP.rows[RFP.order], 
                         ordered = TRUE)

# Ggplot raster with dendro order
RFP.raster <- ggplot(meltPeaks.RFP, aes(time, cell))+
  geom_raster(aes(fill = `Ca2+`))+
  scale_fill_gradientn(colours=c("white", "grey20", "grey10", "black"))+
  theme_pubr()+
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        # axis.ticks.y = element_blank(),
        # axis.text.y = element_text(face=posXY.RFP$Cell[which(posXY.RFP$Member=="TRUE"),], "bold"),
        plot.title = element_text(colour = "red", hjust = .5))+
  ggtitle("ID0032 RFP+", subtitle = sprintf("Mean frequency is: %s events/min", round(frequency.RFP, digits = 3)))

# GRID raster/sums
plots <- align_plots(RFP.raster, RFPsum.plt, align = 'v', axis = 'l')
RFP.grid <- plot_grid(plots[[1]], RFPsum.plt, ncol = 1, rel_heights = c(3.5,1))


# RFPcells for activity/hc/raster/dendrogram using thresholded data  -------------------------------

# Raster ggplot
dfpeaks.RFPt <- as.data.frame(t(RFPt))
# colnames(dfpeaks.RFP) <- 1:ncol(dfpeaks.RFP)
dfpeaks.RFPt$time <- 0:(nrow(dfpeaks.RFPt)-1)
meltPeaks.RFPt <- melt(dfpeaks.RFPt, id = "time")
colnames(meltPeaks.RFPt) <- c('time','cell','Ca2+')

# Hierarchical clustering
hc.RFPt <- hclust(dist(RFPt, method = "euclidean"), method = "ward.D2")
dhc.RFPt <- as.dendrogram(hc.RFPt)

# Dendrogram
RFPt.dendro <- ggdendrogram(dhc.RFPt, rotate = TRUE, labels = FALSE)+
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank())

# GRID to put together dendrograms and rasters
RFPt.order <- order.dendrogram(dhc.RFPt)

## Order the levels according to their position in the cluster
RFPt.rows <- rownames(RFPt)
RFPt.rows <- as.data.frame(RFPt.rows)
meltPeaks.RFPt$cell <- factor(x = meltPeaks.RFPt$cell,
                             levels = RFPt.rows$RFPt.rows[RFPt.order], 
                             ordered = TRUE)

# Ggplot rasterwith dendro order
RFPt.raster <- ggplot(meltPeaks.RFPt, aes(time, cell))+
  geom_raster(aes(fill = `Ca2+`))+
  scale_fill_gradientn(colours=c("white", "grey20", "grey10", "black"))+
  theme_pubr()+
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        # axis.ticks.y = element_blank(),
        # axis.text.y = element_text(face=posXY.RFP$Cell[which(posXY.RFP$Member=="TRUE"),], "bold"),
        plot.title = element_text(colour = "red", hjust = .5))+
  ggtitle("ID0032 RFP+", subtitle = sprintf("Mean frequency is: %s events/min", round(frequency.RFP, digits = 3)))

# GRID raster/sums
plots <- align_plots(RFPt.raster, RFPsum.plt, align = 'v', axis = 'l')
RFPt.grid <- plot_grid(plots[[1]], RFPsum.plt, ncol = 1, rel_heights = c(3.5,1))


# max_CCF()
# Using thresholded values ------------------------------------------------
# # Function to find max CCF between a and b in ±1 lag range
max_CCF<- function(a,b)
{
  d <- ccf(a, b, plot = FALSE, lag.max = 1)
  cor = d$acf[,,1]
  return(max(cor))
} 
# Create empty matrix that will host corr coefficents. 
T.allcellst <- t(spksthresholded)

nc <- nrow(spksthresholded)
cmat.allcellst <- matrix(NA,nc,nc)

# Parallization
library(foreach)
library(doParallel)

pb <- txtProgressBar(min = 0, max = nc, style = 3)
for (i in 1:nc) {
  for (j in 1:nc) {
    cmat.allcellst[i,j] <- max_CCF(T.allcellst[,i],T.allcellst[,j])
    setTxtProgressBar(pb, i)
  }
}
close(pb)

cmat.allcellst[is.na(cmat.allcellst)] <- 0 #(Temporary fix) NaN replaced with 0. This happens when manually adding a ROI on Suite2p mistakenly results in a constant time-series of zeroes (hence ccf() tries to divide by 0)


# Create empty matrix that will host corr coefficents. 
T.RFPt <- t(RFPt)

nc <- nrow(RFPt)
cmat.RFPt <- matrix(NA,nc,nc)


pb <- txtProgressBar(min = 0, max = nc, style = 3)
for (i in 1:nc) {
  for (j in 1:nc) {
    cmat.RFPt[i,j] <- max_CCF(T.RFPt[,i],T.RFPt[,j])
    setTxtProgressBar(pb, i)
  }
}
close(pb)

# Graph
library(ggplot2)
library(igraph)
library(ggraph)
library(visNetwork) 
library(tidyverse)
library(tidygraph)
library(ggiraph)
library(ggnewscale)
library(grid)
library(gridExtra)
library(RColorBrewer)
library(pals)

# AKT1/HRAS cells graph

graph.RFP <- graph.adjacency(as.matrix(cmat.RFPt), mode = "undirected", weighted = TRUE, diag = FALSE) # using thresholded values

# Threshold correlation degree. An interval is chosen because the Pearson correlation coeff goes -1 to 1, BUT -1 means anti-correlation.. so one neuron is active when the other isn't)
# Set weight threshold (set to 0.30 as per literature: Avitan et al., 2017 http://dx.doi.org/10.1016/j.cub.2017.06.056)
graph.RFP <- delete.edges(graph.RFP, which(E(graph.RFP)$weight <0.30))

# Robustness
# cohesion <- cohesion(graph.RFP)


# Communities detection ---------------------------------------------------
# greedy method (hierarchical, fast method)
graph.clusters.RFP = cluster_leading_eigen(graph.RFP)
posXY.RFP$Community <- graph.clusters.RFP$membership

# Number of degrees per community?

# test <- posXY.RFP %>% 
#     group_by(Community) %>%
#     summarise(Degree = sum(Degree))

# Clustering coefficient RFP
ID0032.clustcoeff.RFP <- transitivity(graph.RFP)

# Global efficiency RFP (NaN if there are no connected triples in the graph)
ID0032.globaleff.RFP <- global_efficiency(graph.RFP)



# Network plot ------------------------------------------------------------
# Make composite palette
colorz = grDevices::colors()[grep('gr(a|e)y', grDevices::colors(), invert = T)]
communities.guide <- guide_legend(title = element_text("Communities"),
                                  label = FALSE,
                                  keywidth = 0.1)

graph.RFP.plt <- ggraph(graph.RFP, 
                                          layout = as.matrix(posXY.RFP)[, c("X", "Y")]) +
                                          geom_edge_link(aes(colour = weight, alpha = weight))+
                                          scale_edge_alpha_continuous(range = c(0.1, 1), guide = "none")+
                                          scale_edge_color_viridis(name = "F. Corr",
                                                                   alpha = 1,
                                                                   begin = 0.3,
                                                                   end = 1,
                                                                   discrete = FALSE,
                                                                   option = "inferno",
                                                                   direction = 1
                                          )+
                                          # Calcium levels and degrees
                                          geom_node_point(aes(fill = ordered(cluster_leading_eigen(graph.RFP)$membership),
                                                              size = degree(graph.RFP)),
                                                          shape = 21)+
                                          # geom_node_text(aes(label = posXY.RFP$Cell), 
                                          #                colour = "red",
                                          #                 repel = TRUE,
                                          #                size = 2.5)+
                                          geom_node_text(aes(label = ordered(cluster_leading_eigen(graph.RFP)$membership)),
                                                         colour = "black",
                                                         fontface = 1,
                                                         size = 3)+
                                          scale_fill_manual(values = colorz,
                                                            guide = "none")+
                                          scale_size_continuous(range = c(5, 12),
                                                            guide = "none")+
                                          # scale_shape_manual(values = c("TRUE" = 25, "FALSE" = 21))+
                                          # scale_colour_manual(values = c("TRUE" = "#fc9272", "FALSE" = "black"))+
                                          # labs(fill = "Ca")+
                                          # Hubs
                                          # annotate("text", x=45, y=20, 
                                          #           label = "W. thresh. = 0.50")+
                                          # annotate("text", x=40, y=35,
                                          #          label = "Cohesion = ")+
                                          # annotate("text", x=70, y=35,
                                          #          label = cohesion)+
                                          # geom_node_point(aes(fill = as.factor(posXY$synchron),
                                          #                     size = as.factor(posXY$synchron),
                                          #                     shape = as.factor(posXY$synchron)))+
                                          # scale_size_manual(values = g.sizes.Sync, name = "Synchronous")+
                                          # scale_fill_manual(values = g.palette.Sync, name = "Synchronous")+
                                          # scale_shape_manual(values = g.shapes.Sync, name = "Synchronous")+
                                          # geom_node_label(aes(label = posXY$Cell), repel = TRUE)+
                                          
                                          theme_graph(background = "white",
                                                      plot_margin = margin(5, 5, 5, 5))+
                                          theme(legend.position = "right",
                                                legend.margin	= margin(1,1,1,1),
                                                legend.key.size = unit(0.5, 'cm'), #change legend key size
                                                # legend.key.height = unit(1, 'pt'), #change legend key height
                                                # legend.key.width = unit(1, 'pt'), #change legend key width
                                                # legend.title = element_text(size=5), #change legend title font size
                                                # legend.text = element_text(size=4),
                                                # legend.text.align = 0
                                          )+
                                          ggtitle("ID0032 RFP+")+
                                          scale_y_reverse() #this is because in images/movies y axis in coordinates is reversed



# Histogram count of degrees ----------------------------------------------
posXY.RFP$Degree <- degree(graph.RFP)
max.y.degree <- length(RFPcells)

degree.RFP.hist <- gghistogram(posXY.RFP, x = "Degree", y = "..count..",
                                      binwidth = 1)


# Mean degree
degree.mean.RFP <- mean(degree(graph.RFP))


# # libs for PCA --------------------------------------------------------------------
# library(factoextra)
# library(ggpubr)
# library(ggfortify)
# # PCA ---------------------------------------------------------------------
# # General population
# pca <- prcomp(spksthresholded, center = TRUE, scale = FALSE) # change to scale = FALSE if not normalised data
# scree <- fviz_eig(pca, ncp = 100)
# scree <- ggpar(scree, title = element_blank())
# ID0032.pca.eigenvalues <- get_eigenvalue(pca)
# 
# # for RFP
# pca.RFP <- prcomp(RFPt, center = TRUE, scale = FALSE) # change to scale = FALSE if not normalised data
# scree.RFP <- fviz_eig(pca.RFP, ncp = 100)
# scree.RFP <- ggpar(scree.RFP, title = element_blank())
# ID0032.pca.RFP.eigenvalues <- get_eigenvalue(pca.RFP)


# Viz ---------------------------------------------------------------------
gs = c(graph.RFP.plt, degree.RFP.hist,
      RFP.grid, RFPsum2.plt)

lay <- rbind(c(1,1,3,3),
             c(1,1,3,3),
             c(2,5,4,4))
arranged <- grid.arrange(graph.RFP.plt, degree.RFP.hist,
                     RFP.grid, RFPsum2.plt,
                     layout_matrix = lay)


#Save whole graph + raster + activity plot + coactive cells/time
ggsave(plot = arranged, file = "/Users/Simo/calcium-clustering/plots/ID0032.whole.RFP.png", 
       device = "png",  bg = "white",
       width = 20, height = 15, units = "cm", dpi = 320,
       scale = 2)


# General graph2

graph <- graph.adjacency(as.matrix(cmat.allcellst), mode = "undirected", weighted = TRUE, diag = FALSE) # using thresholded values

# Threshold correlation degree. An interval is chosen because the Pearson correlation coeff goes -1 to 1, BUT -1 means anti-correlation.. so one neuron is active when the other isn't)
# Set weight threshold (set to 0.30 as per literature: Avitan et al., 2017 http://dx.doi.org/10.1016/j.cub.2017.06.056)
graph <- delete.edges(graph, which(E(graph)$weight <0.30))

# Robustness
# cohesion <- cohesion(graph)

# Communities detection ---------------------------------------------------
# greedy method (hierarchical, fast method)
graph.clusters = leading.eigenvector.community(graph, options = list(maxiter = 1000000))
posXY$Community <- graph.clusters$membership



# Clustering coefficient RFP
ID0032.clustcoeff <- transitivity(graph)

# Global efficiency RFP
ID0032.globaleff <- global_efficiency(graph)


# Network plot ------------------------------------------------------------
# Make composite palette
colorz = grDevices::colors()[grep('gr(a|e)y', grDevices::colors(), invert = T)]
colorz.invert = rev(colorz)
communities.palette.big <- c(colorz, brewer.pal(9,'Set1'),
                         brewer.pal(8,'Set2'),
                         brewer.pal(12,'Set3'),
                         brewer.pal(8, 'Dark2'),
                         brewer.pal(8, 'Accent'),
                         brewer.pal(9,'Pastel1'),
                         colorz.invert, colorz)

communities.guide <- guide_legend(title = element_text("Communities"),
                                  label = FALSE,
                                  keywidth = 0.1)

graph.plt <- ggraph(graph, 
                                          layout = as.matrix(posXY)[, c("X", "Y")]) +
                                          geom_edge_link(aes(colour = weight, alpha = weight))+
                                          scale_edge_alpha_continuous(range = c(0.1, 1), guide = "none")+
                                          scale_edge_color_viridis(name = "F. Corr",
                                                                   alpha = 1,
                                                                   begin = 0.3,
                                                                   end = 1,
                                                                   discrete = FALSE,
                                                                   option = "inferno",
                                                                   direction = 1
                                          )+
                                          # Calcium levels and degrees
                                          geom_node_point(aes(fill = ordered(leading.eigenvector.community(graph, options = list(maxiter = 1000000))$membership),
                                                              size = degree(graph)),
                                                          shape = 21)+
                                          # geom_node_text(aes(label = posXY$Cell), 
                                          #                colour = "red",
                                          #                 repel = TRUE,
                                          #                size = 2.5)+
                                          geom_node_text(aes(label = ordered(leading.eigenvector.community(graph, options = list(maxiter = 1000000))$membership)),
                                                         colour = "black",
                                                         fontface = 1,
                                                         size = 3)+
                                          scale_fill_manual(values = communities.palette.big,
                                                            guide = "none")+
                                          scale_size_continuous(range = c(5, 12),
                                                            guide = "none")+
                                          # scale_shape_manual(values = c("TRUE" = 25, "FALSE" = 21))+
                                          # scale_colour_manual(values = c("TRUE" = "#fc9272", "FALSE" = "black"))+
                                          # labs(fill = "Ca")+
                                          # Hubs
                                          # annotate("text", x=45, y=20, 
                                          #           label = "W. thresh. = 0.50")+
                                          # annotate("text", x=40, y=35,
                                          #          label = "Cohesion = ")+
                                          # annotate("text", x=70, y=35,
                                          #          label = cohesion)+
                                          # geom_node_point(aes(fill = as.factor(posXY$synchron),
                                          #                     size = as.factor(posXY$synchron),
                                          #                     shape = as.factor(posXY$synchron)))+
                                          # scale_size_manual(values = g.sizes.Sync, name = "Synchronous")+
                                          # scale_fill_manual(values = g.palette.Sync, name = "Synchronous")+
                                          # scale_shape_manual(values = g.shapes.Sync, name = "Synchronous")+
                                          # geom_node_label(aes(label = posXY$Cell), repel = TRUE)+
                                          
                                          theme_graph(background = "white",
                                                      plot_margin = margin(5, 5, 5, 5))+
                                          theme(legend.position = "right",
                                                legend.margin	= margin(1,1,1,1),
                                                legend.key.size = unit(0.5, 'cm'), #change legend key size
                                                # legend.key.height = unit(1, 'pt'), #change legend key height
                                                # legend.key.width = unit(1, 'pt'), #change legend key width
                                                # legend.title = element_text(size=5), #change legend title font size
                                                # legend.text = element_text(size=4),
                                                # legend.text.align = 0
                                          )+
                                          ggtitle("ID0032")+
                                          scale_y_reverse() #this is because in images/movies y axis in coordinates is reversed

# Save graph
ggsave(plot = graph.plt, file = "/Users/Simo/calcium-clustering/plots/ID0032.graph.png", 
       device = "png",  bg = "white",
       width = 20, height = 15, units = "cm", dpi = 320,
       scale = 2)

# Connections between normal and RFP+ cells
graph.btw.plt <- ggraph(graph, 
                                          layout = as.matrix(posXY)[, c("X", "Y")]) +
                                          geom_edge_link(aes(colour = weight, alpha = weight))+
                                          scale_edge_alpha_continuous(range = c(0.1, 1), guide = "none")+
                                          scale_edge_color_viridis(name = "F. Corr",
                                                                   alpha = 1,
                                                                   begin = 0.3,
                                                                   end = 1,
                                                                   discrete = FALSE,
                                                                   option = "inferno",
                                                                   direction = 1
                                          )+
                                          # Calcium levels and degrees
                                          geom_node_point(aes(fill = as.factor(posXY$redcell),
                                                              size = as.factor(posXY$redcell)),
                                                          shape = 21)+
                                          # geom_node_text(aes(label = posXY$Cell), 
                                          #                colour = "blue",
                                          #                 repel = TRUE,
                                          #                size = 2.5)+
                                         scale_fill_manual(values = c("0" = "grey",
                                                                      "1" = "red"),
                                                            guide = "none")+
                                         scale_size_manual(values = c("0" = 5,
                                                                      "1" = 8),
                                                           guide = "none")+
                                          theme_graph(background = "white",
                                                      plot_margin = margin(5, 5, 5, 5))+
                                          theme(legend.position = "right",
                                                legend.margin	= margin(1,1,1,1),
                                                legend.key.size = unit(0.5, 'cm'), #change legend key size
                                                # legend.key.height = unit(1, 'pt'), #change legend key height
                                                # legend.key.width = unit(1, 'pt'), #change legend key width
                                                # legend.title = element_text(size=5), #change legend title font size
                                                # legend.text = element_text(size=4),
                                                # legend.text.align = 0
                                          )+
                                          ggtitle("ID0032 RFP+ highlighted")+
                                          scale_y_reverse() #this is because in images/movies y axis in coordinates is reversed

# Save graph
ggsave(plot = graph.btw.plt, file = "/Users/Simo/calcium-clustering/plots/ID0032.graph.btw.plt.png", 
       device = "png",  bg = "white",
       width = 20, height = 15, units = "cm", dpi = 320,
       scale = 2)



# PCA
# pca <- prcomp(T.allcellst, center = TRUE, scale = FALSE) # change to scale = FALSE if not normalised data



```
```










```{r dF.npy}
######################################### dF/F #########################################
# Average calcium levels over time ----------------------------------------
## Here by using dF traces after executing "get_dF.py" to extract them
dF <- as.data.frame(np$load("dF.npy", allow_pickle = TRUE)) #delta F calcium levels of all cells
dF <- dF[,50:ncol(dF)] #select window
# dF <- t(apply(dF, 1, function(x) (x - min(x))/(max(x)-min(x)))) # Normalize?
dFPOS <- dF[positivesPLUSone,]
rownames(dFPOS) <- positives
dFPOS
```


```{r average activity/HRAS cell}
# Average activity per RFP+ cell (dF peaks) -------------------------------
posXY$Mean.dF <- rowMeans(dFPOS)
posXY$Mean.dF.N <- apply(as.matrix(posXY$Mean.dF), 2,
                                function(x) (x - min(x))/(max(x)-min(x)))
posXY
```

# ```{r coactive cells percentage/time}
# # Calculating percentage of active RFP+ cells over time --------------------
# dF.RFP <- subset(spksthresholded, rownames(dFPOS) %in% RFPcells) #select only RFP cells
# ##ggplot to show percentage of RPF+ cells over time
# RFPsum <- as.data.frame(colSums(RFP))
# RFPsum$Time <- 0:(nrow(RFPsum)-1)
# RFPsum$Perc <- RFPsum$`colSums(RFP)`/nrow(RFP)*100
# RFPsum.dF.plt <- ggplot(RFPsum, aes(Time, Perc))+
#   geom_line()+
#   theme_pubr()
# RFPsum.dF.plt
# ```


#Averaging per timepoint (all cells)
# dFx <- as.data.frame(colSums(dFPOS)/nrow(dFPOS))
# dFx$Time <- 0:(nrow(dFx)-1)
# #plot
# POS.aveF <- ggplot(dFx, aes(Time, `colSums(dFPOS)/nrow(dFPOS)`))+
#   geom_line()+
#   theme_pubr()+
#   ylab("Average dF/F")+
#   geom_smooth(method = "loess")
# 
# 
# 



# Averaging per timepoint (RFP only)
# FrawRFPx <- as.data.frame(colSums(FrawRFP)/nrow(FrawRFP))
# FrawRFPx$Time <- 0:(nrow(FrawRFPx)-1)
# #plot
# RFP.aveF <- ggplot(FrawRFPx, aes(Time, `colSums(FrawRFP)/nrow(FrawRFP)`))+
#                               geom_line()+
#                               theme_pubr()+
#                               ylab("Average Ca2+ (RFP+)")+
#                               geom_smooth(method = "loess")






# Plot RFP deconvolved curves all together

# POSITION ANALYSIS
# cut3 <- cutree(hc, k = 3)
# 
# posXY$Cluster <- cut3
# 
# ggplot(posXY, aes(X, Y, color = as.factor(Cluster), shape = as.factor(Cluster)))+
#   geom_point(size = 2)+
#   # scale_color_manual(values=c('red','blue','green'))+
#   theme_graph()+
#   scale_y_reverse()







# Color clusters
# put on graph