# Correlation between redcell:total cells ratio VS total events/min

**Aim:** To see if the low number of redcells in some samples is influencing graph features These ratios are stored in "AKT1.redcell.ratio" "CTRL.redcell.ratio" "HRASV12.redcell.ratio" But I also need the events/min vars.. Need to see if there is correlation for ALL conditions, including AGE

example code to collect the vars:

```{r example code}
# Create a vector of variable names from different ranges
var_names <- c(
  paste0("ID0", 130:132, "redcell.ratio"),
  paste0("ID0", 139:143, "redcell.ratio")
)

# Use mget to retrieve values of these variables from the environment
values <- mget(var_names)

# Combine all values into HRASV12_5dpf.redcell.ratio
AKT1_5dpf.redcell.ratio <- unlist(values)
AKT1_5dpf.redcell.ratio

# For the frequency values:
all_AKT1_5dpf_freq <- c(
    all_lists[["AKT1_5dpf_hind"]][grepl(pattern, names(all_lists[["AKT1_5dpf_hind"]]), perl = TRUE)], 
    all_lists[["AKT1_5dpf_mid"]][grepl(pattern, names(all_lists[["AKT1_5dpf_mid"]]), perl = TRUE)]
)

# order them so they parallel each other
# Sort AKT1_5dpf.redcell.ratio by the names
AKT1_5dpf.redcell.ratio <- AKT1_5dpf.redcell.ratio[order(names(AKT1_5dpf.redcell.ratio))]

# Sort all_AKT1_5dpf_freq by the names
all_AKT1_5dpf_freq <- all_AKT1_5dpf_freq[order(names(all_AKT1_5dpf_freq))]

```

Correlation analysis VS events/min (frequency):

```{r frequency}
correlation_result_CTRL_4dpf.freq <- cor.test(as.numeric(CTRL_4dpf.redcell.ratio), as.numeric(all_CTRL_4dpf_freq))
correlation_result_CTRL_5dpf.freq <- cor.test(as.numeric(CTRL_5dpf.redcell.ratio), as.numeric(all_CTRL_5dpf_freq))


correlation_result_HRASV12_4dpf.freq <- cor.test(as.numeric(HRASV12_4dpf.redcell.ratio), as.numeric(all_HRASV12_4dpf_freq))
correlation_result_HRASV12_5dpf.freq <- cor.test(as.numeric(HRASV12_5dpf.redcell.ratio), as.numeric(all_HRASV12_5dpf_freq))

correlation_result_AKT1_4dpf.freq <- cor.test(as.numeric(AKT1_4dpf.redcell.ratio), as.numeric(all_AKT1_4dpf_freq))
correlation_result_AKT1_5dpf.freq <- cor.test(as.numeric(AKT1_5dpf.redcell.ratio), as.numeric(all_AKT1_5dpf_freq))

# Print the correlation coefficient and p-value
print(paste0("CTRL 4dpf ", correlation_result_CTRL_4dpf.freq$p.value))
print(paste0("CTRL 5dpf ", correlation_result_CTRL_5dpf.freq$p.value))
print(paste0("HRASV12 4dpf ", correlation_result_HRASV12_4dpf.freq$p.value))
print(paste0("HRASV12 5dpf ", correlation_result_HRASV12_5dpf.freq$p.value))
print(paste0("AKT1 4dpf ", correlation_result_AKT1_4dpf.freq$p.value))
print(paste0("AKT1 4dpf ", correlation_result_AKT1_5dpf.freq$p.value))
```

Correlation analysis VS mean (deconvoluted) Calcium levels

```{r mean_Ca}
correlation_result_CTRL_4dpf.ca <- cor.test(as.numeric(CTRL_4dpf.redcell.ratio), as.numeric(CTRL_4dpf__mean_Ca))
correlation_result_CTRL_5dpf.ca <- cor.test(as.numeric(CTRL_5dpf.redcell.ratio), as.numeric(CTRL_5dpf__mean_Ca))

correlation_result_HRASV12_4dpf.ca <- cor.test(as.numeric(HRASV12_4dpf.redcell.ratio), as.numeric(HRASV12_4dpf__mean_Ca))
correlation_result_HRASV12_5dpf.ca <- cor.test(as.numeric(HRASV12_5dpf.redcell.ratio), as.numeric(HRASV12_5dpf__mean_Ca))

correlation_result_AKT1_4dpf.ca <- cor.test(as.numeric(AKT1_4dpf.redcell.ratio), as.numeric(AKT1_4dpf__mean_Ca))
correlation_result_AKT1_5dpf.ca <- cor.test(as.numeric(AKT1_5dpf.redcell.ratio), as.numeric(AKT1_5dpf__mean_Ca))

print(paste0("CTRL 4dpf ", correlation_result_CTRL_4dpf.ca$p.value))
print(paste0("CTRL 5dpf ", correlation_result_CTRL_5dpf.ca$p.value))
print(paste0("HRASV12 4dpf ", correlation_result_HRASV12_4dpf.ca$p.value))
print(paste0("HRASV12 5dpf ", correlation_result_HRASV12_5dpf.ca$p.value))
print(paste0("AKT1 4dpf ", correlation_result_AKT1_4dpf.ca$p.value))
print(paste0("AKT1 4dpf ", correlation_result_AKT1_5dpf.ca$p.value))
```
